---
title: "p8105_hw1_fl2715"
author: "Fengwei Lei"
output: github_document
---

Firstly, we load necessary library *tidyverse* for Problem 1 and 2.
```{r, include=FALSE}
library(tidyverse)
```

# Problem 1
## *1.1 Load Penguins  Dataset*
We load the "penguins" dataset from the package "palmerpenguins".
```{r, include=FALSE}
data("penguins", package = "palmerpenguins")
```

## *1.2 Description of the Penguins Dataset*
The penguins dataset contains data on three penguin species (`r unique(pull(penguins,species))`), which were collected from 3 islands (`r unique(pull(penguins,island))`) between `r min(pull(penguins,year))` and `r max(pull(penguins,year))`. The other important variables include bill length (bill_length_mm), bill depth (bill_depth_mm), flipper length (flipper_length_mm) and body mass (body_mass_g). This dataset consists of `r nrow(penguins)` rows and `r ncol(penguins)` columns. And the mean flipper length of the penguins is `r mean(pull(penguins,flipper_length_mm), na.rm = TRUE)` mm.
